Co-citations in context

### 2019-05-24 cocit_r.tex
update Section Chacko

\begin{document}
\title[Co-citations in context]{Co-citations in context}
\subtitle{Disciplinary heterogeneity is relevant}

@@

\section{Results}
\subsection{Chacko}
(i) disciplinary networks are different
(ii) background makes a difference
(iii) 
(iv)

@@

\acknowledgments
We are grateful to Kevin Boyack and Dick Klavans for critically constructive discussions. We thank the authors of Uzzi et al. (2013) for sharing their Python simulation code. Research and development reported in this publication was partially supported by Federal funds from the National Institute on Drug Abuse, National Institutes of Health, US Department of Health and Human Services, under Contract Nos. HHSN271201700053C (N43DA-17-1216) and HHSN271201800040C (N44DA-18-1216). The content of this publication is solely the responsibility of the authors and does not necessarily represent the official views of the National Institutes of Health. TW receives funding from the Grainger Foundation. All the code used in this study is freely available from a Github site. Access to the bibliographic data analyzed in this study requires a license from Clarivate Analytics, which had no role in funding, experimental design, review of results, and conclusions presented.

>>>>

\begin{document}
\title[Co-citations in context]{Co-citations in context}
\subtitle{disciplinary heterogeneity is relevant}

@@

\section{Results}
\subsection{Chacko} In our study, we also use a Monte Carlo approach to simulate under a random graph model. A  principal consideration, however, was to restrict model misspecification arising from disciplinarily irrelevant references. We addressed this consideration by restricting random substitutions to only those references in the disciplinary network being studied. We estimated model misspecification by measuring the Kullback-Leibler (K-L) Divergence~\citep{kullback_information_1951} between observed and simulated frequencies for the set of journals common to both a disciplinary network and the WoS superset (Table 3). The results indicate that simulations under our model consistently have a lower K-L divergence compared to simulations that draw from the WoS superset and its attendant substitutions that are ectopic with respect to field and discipline (Introduction).

\begin{table}[ht]
\caption{Measuring Model Misspecification. For the set of journal pairs in common between a disciplinary network and the full WoS dataset, Kullback-Leibler (K-L) divergences
between empirical and simulated journal pair frequencies were computed for the years 1985, 1995, and 2005 for the three disciplinary datasets (applied\_physics, immunology, and metabolism) using either the disciplinary network as background or the WoS superset (all\_wos) to generate the null model (Background). K-L divergence was calculated using the R seewave package with a base (logarithm) of 2. The ratio between the K-L divergence for disciplinary networks versus the full WoS ranges from 1.96 to 2.77 and is greater than 2.0 for eight out of nine cases, strongly suggesting that simulations that constrain substitutions to the given disciplinary network better model the observed data.}
\label{tab:label}
\centering
\begin{tabular}{|r lrlr r|}
  \hline
 & Disciplinary Network & Year & Background & K-L Divergence & Ratio \\ 
  \hline
1 & appl\_physics & 1985 & appl\_physics & 1.21 &  \\ 
  2 &  & 1985 & all\_wos & 2.37 & 1.96 \\ 
  3 &  & 1995 & appl\_physics & 0.86 &  \\ 
  4 &  & 1995 & all\_wos & 2.37 & 2.77 \\ 
  5 &  & 2005 & appl\_physics & 0.95 &  \\ 
  6 &  & 2005 & all\_wos & 2.35 & 2.47 \\ 
    \hline
  7 & immunology & 1985 & immunology & 0.75 &  \\ 
  8 &  & 1985 & all\_wos & 1.68 & 2.24 \\ 
  9 &  & 1995 & immunology & 0.78 &  \\ 
  10 &  & 1995 & all\_wos & 1.70 & 2.19 \\ 
  11 &  & 2005 & immunology & 0.73 &  \\ 
  12 &  & 2005 & all\_wos & 1.92 & 2.63 \\ 
    \hline
  13 & metabolism & 1985 & metabolism & 1.11 &  \\ 
  14 &  & 1985 & all\_wos & 2.24 & 2.02 \\ 
  15 &  & 1995 & metabolism & 1.07 &  \\ 
  16 &  & 1995 & all\_wos & 2.33 & 2.17 \\ 
  17 &  & 2005 & metabolism & 1.19 &  \\ 
  18 &  & 2005 & all\_wos & 2.60 & 2.18 \\ 
   \hline
\end{tabular}
\end{table}

\begin{figure}
\includegraphics[width=\hsize]{Fig1}
\caption{Fraction of publications with high conventionality (HC) and high novelty (HN) signatures relative to citation count.}
\end{figure}

@@

\acknowledgments
We are grateful to Kevin Boyack and Dick Klavans for constructively critical discussions. We thank the authors of Uzzi et al. (2013) for sharing their Python simulation code. Research and development reported in this publication was partially supported by Federal funds from the National Institute on Drug Abuse, National Institutes of Health, US Department of Health and Human Services, under Contract Nos. HHSN271201700053C (N43DA-17-1216) and HHSN271201800040C (N44DA-18-1216). The content of this publication is solely the responsibility of the authors and does not necessarily represent the official views of the National Institutes of Health. TW receives funding from the Grainger Foundation. All the code used in this study is freely available from a Github site. Access to the bibliographic data analyzed in this study requires a license from Clarivate Analytics, which had no role in funding, experimental design, review of results, and conclusions presented.
